\begin{thebibliography}{99}
\bibitem{ref1} Baruch M., Baruch G., Goldberg Y. (2019), "A little is enough: Circumventing defenses for distributed learning", Advances in Neural Information Processing Systems (NeurIPS), Vol.32.
\bibitem{ref2} Blanchard P., El Mhamdi E. M., Guerraoui R., Stojanovic R. J. (2017), "Machine learning with adversaries: Byzantine tolerant gradient descent", Advances in Neural Information Processing Systems (NeurIPS), Vol.30.
\bibitem{ref3} Cao W., Gong X. Y., Zhenqiang N. (2022), "MPAF: Model poisoning attacks to federated learning based on fake clients", Proc. IEEE/CVF Conference on Computer Vision and Pattern Recognition Workshops (CVPRW), pp.3396--3404.
\bibitem{ref4} Gulrajani I., Ahmed F., Arjovsky M., Dumoulin V., Courville A. C. (2017), "Improved training of Wasserstein GANs", Advances in Neural Information Processing Systems (NeurIPS), pp.5767--5777.
\bibitem{ref5} Issa W., Moustafa N., Turnbull B., Choo K.-K. R. (2025), "DT-BFL: Digital twins for blockchain-enabled federated learning in Internet of Things networks", Ad Hoc Networks, Vol.165, Art. no.103632.
\bibitem{ref6} Jolicoeur-Martineau A., Fatras K., Kachman T. (2024), "Generating and imputing tabular data via diffusion and flow-based gradient-boosted trees", Proc. 27th International Conference on Artificial Intelligence and Statistics (AISTATS), pp.1288--1296.
\bibitem{ref7} Kotelnikov A., Baranchuk D., Rubachev I., Babenko A. (2023), "TabDDPM: Modelling tabular data with diffusion models", Proc. 40th International Conference on Machine Learning (ICML), pp.17564--17579.
\bibitem{ref8} Lu Y., Huang X., Zhang K., Maharjan S., Zhang Y. (2020), "Communication-efficient federated learning and permissioned blockchain for digital twin edge networks", IEEE Internet of Things Journal, Vol.8 (4), pp.2276--2288.
\bibitem{ref9} McMahan B., Moore E., Ramage D., Hampson S., Arcas B. A. (2017), "Communication-efficient learning of deep networks from decentralized data", Proc. 20th International Conference on Artificial Intelligence and Statistics (AISTATS), pp.1273--1282.
\bibitem{ref10} Moustafa N. (2021), "A new distributed architecture for evaluating AI-based security systems at the edge: Network TON\_IoT datasets", Sustainable Cities and Society, Vol.72, Art. no.102994.
\bibitem{ref11} Neto E. C. P., Dadkhah S., Ferreira R., Zohourian A., Lu R., Ghorbani A. A. (2023), "CICIoT2023: A real-time dataset and benchmark for large-scale attacks in IoT environment", Sensors, Vol.23 (13), Art. no.5941.
\bibitem{ref12} Pillutla K., Kakade S. M., Harchaoui Z. (2022), "Robust aggregation for federated learning", IEEE Transactions on Signal Processing, Vol.70, pp.1142--1154.
\bibitem{ref13} Qu Y., Pokhrel S., Nepal S., Gao L., Xiang Y. (2021), "Decentralized privacy using blockchain-enabled federated learning in fog computing", IEEE Internet of Things Journal, Vol.8 (8), pp.6521--6533.
\bibitem{ref14} Shapley L. S. (1953), "A value for n-person games", Contributions to the Theory of Games II, Princeton University Press, Princeton, NJ, USA, pp.307--317.
\bibitem{ref15} Shejwalkar V., Houmansadr A. (2021), "Manipulating the Byzantine: Optimizing model poisoning attacks and defenses for federated learning", Proc. 28th Network and Distributed System Security Symposium (NDSS).
\bibitem{ref16} Xu J., Huang S.-L., Song L., Lan T. (2022), "SignGuard: Byzantine-tolerant federated learning through collaborative malicious gradient filtering", Proc. IEEE 42nd International Conference on Distributed Computing Systems (ICDCS), pp.530--540.
\bibitem{ref17} Xu L., Skoularidou M., Cuesta-Infante A., Veeramachaneni K. (2019), "Modeling tabular data using conditional GAN", Advances in Neural Information Processing Systems (NeurIPS), Vol.32.
\bibitem{ref18} Yin D., Chen Y., Kannan R., Bartlett P. (2018), "Byzantine-robust distributed learning: Towards optimal statistical rates", Proc. 35th International Conference on Machine Learning (ICML), pp.5650--5659.
\bibitem{ref19} Zeng Y. et al. (2024), "ClipCluster: A defense against Byzantine attacks in federated learning", IEEE Transactions on Information Forensics and Security, Vol.19, pp.4567--4581.
\bibitem{ref20} Zhang H., Zhang J., Srinivasan B., Shen Z., Qin X., Faloutsos C. (2024), "Mixed-type tabular data synthesis with score-based diffusion in latent space", Proc. 12th International Conference on Learning Representations (ICLR).
\bibitem{ref21} Zhang X., Liu H., Yang F. (2025), "Enhanced traffic carbon emissions data sharing and modeling via blockchain and personalized federated learning in IIoT ecosystem", IEEE Internet of Things Journal, Vol.12 (15), pp.31064--31078.
\bibitem{ref22} Zhang Z., Peng H., Li L., Bao S. (2025), "Adaptive asynchronous federated learning for digital twin driven smart grid", IEEE Transactions on Smart Grid, Vol.16 (5), pp.4167--4181.
\bibitem{ref23} Pham Hoang Hao, Phan The Duy, Pham Van-Hau (2026), "Active Digital Twin Verification for Robust Federated Learning in IoT Intrusion Detection", Proc. 2026 Eleventh International Conference on Communications and Electronics (ICCE 2026) --- Communication Networks and Systems, IEEE, Nha Trang, Vietnam.
\end{thebibliography}
